Circumnuclear Media of Quiescent Supermassive Black Holes

### 2015-06-26 ms.tex
typo
Adding referee acknowledgement.
angular momentum discussion and eqn typo.

\begin{equation}
v_w > {\rm max}[v_{\rm TI},\sigma_0\{1-(r_{b}/r_{\rm
  inf})^{0.5(1-\Gamma)}\}]
\label{eq:cooling4}
\end{equation}

Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass
input parameters $\eta$, as well as the [$\eta$-independent] $\zeta >
\zeta_c$ criterion, shown separately for cusp and core galaxies.
Based on the \citet{LauerFaber+:2007a} sample we take $\rinf = 25(8)M
0.6$ pc and $\rb = 106 \Mbheight^{0.4}$ (100 pc) and thus
$\rb/\rinf\simeq 4 \Mbheight^{-0.2} (13 \Mbheight^{-0.6})$ for cores
(cusps).  For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$
criterion is generally more stringent, while for core galaxies the
$\zeta > \zeta_c$ criterion is more strigent for core galaxies, except
for high mass loss rates $\eta > 1$.

@@

\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$
is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy
half-light radius and that $\lambda_R$ decreases with decreasing $R$
interior to this point.  From equation (\ref{eq:rcirc}) we thus
conclude that $r_{\rm circ} \lesssim 0.01r_{s}$, i.e.~that gas will
most likely circularize within the inner sonic point of the flow
(Fig.~\ref{fig:profiles}).  Angular momentum should only become
dynamically important for thermally stable flows in a region that is
causally disconnected from the outer part of the flow. Thus, the flow
properties on large scales will generally be unaffected by angular
momentum.

@@

where we implicitly the different sources of energy injection mix
efficiently. In reality, this may not be the case as slower velocity
sources cool and form high density structure due to high pressure from
the environment\citep{Cuadra+2005}.

@@

We acknowledge helpful conversations with Greg Bryan, Jenny Greene,
Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot Quataert.
This work relied on Columbia University's Yeti computer cluster, and
we acknowledge the Columbia HPC support staff for assistance.  BDM
gratefully acknowledges support from NASA {\it Fermi} grant
NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan Foundation.

>>>>

\begin{equation}
v_w > {\rm max}[v_{\rm TI},\sigma_0\{(r_{b}/r_{\rm
  inf})^{(1-\Gamma)}-1\}^{1/2}\}]
\label{eq:cooling4}
\end{equation}

Figure \ref{fig:TI} shows $v_{\rm TI}(M_{\bullet})$ for different mass
input parameters $\eta$, as well as the [$\eta$-independent] $\zeta >
\zeta_c$ criterion, shown separately for cusp and core galaxies.
Based on the \citet{LauerFaber+:2007a} sample we take $\rinf = 25(8)M
^{0.6}$ pc and $\rb = 106 \Mbheight^{0.4}$ (100 pc) and thus
$\rb/\rinf\simeq 4 \Mbheight^{-0.2} (13 \Mbheight^{-0.6})$ for cores
(cusps).  For cusp galaxies we see that the $v_w \gtrsim v_{\rm TI}$
criterion is generally more stringent, while for core galaxies the
$\zeta > \zeta_c$ criterion is more strigent for core galaxies, except
for high mass loss rates $\eta > 1$.

@@

\citet{EmsellemCappellari+:2007a} (their Fig.~2) find that $\lambda_R$
is generally $< 0.1$ on radial scales $<$ 10 per cent of the galaxy
half-light radius and that $\lambda_R$ decreases with decreasing $R$
interior to this point.  From equation (\ref{eq:rcirc}) we thus
conclude that $r_{\rm circ} \lesssim 0.01r_{s}$. For the low inflow
rates considered the gas ($\eddr<0.01$) would be unable to cool on a
dynamical time and would likely drive a bipolar outflow
\citep{Li+2013}. Our model cannot capture such two dimensional
structures, but would still be relevant for large scale flow
properties in regions where the gas is inflowing.

@@

where we implicitly assume the different sources of energy injection mix
efficiently. In reality, this may not be the case as slower velocity
sources cool and form high density structure due to high pressure from
the environment\citep{Cuadra+2005}.

@@

We thank the referee, Sergei Nayakshin, for several insightful
comments. We acknowledge helpful conversations with Greg Bryan, Jenny
Greene, Jules Halpern, Kathryn Johnston, Jerry Ostriker, and Eliot
Quataert.  This work relied on Columbia University's Yeti computer
cluster, and we acknowledge the Columbia HPC support staff for
assistance.  BDM gratefully acknowledges support from NASA {\it Fermi}
grant NNX14AQ68G, NSF grant AST-1410950, and the Alfred P. Sloan
Foundation.

### 2015-06-26 windheat.tex
angular momentum discussion and eqn typo.

In the case of a single impulsive burst of star formation, the mass
and energy injection rate per unit stellar mass at time $t$ after the
burst are given, respectively, by
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
        T}(t)}
    \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar }{\bar{m}_*}\\
  \dot{\bar{e}}(t) &=\dot{e}_{\rm TO}(t)+ f_{\rm MS} \int_{m_0}^{m_{\rm T}(t)}
  \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
  \label{eq:edotImp}
\end{align} 
where the first and second terms in each expression corresponds to
contributions from main sequence (MS) stars and post-main sequence
(PMS) stars, respectively.  Here $ f_{\rm MS} < 1$ is the efficiency
with which main sequence winds thermalize their energy with the rest
of the injected gas (we hereafter assume $f_{\rm MS} = 1$) and $\mu$
is the IMF, which we take to be of the Salpeter form $\mu|_{\Mstar}
\propto M_{\star}^{-2.35}$, truncated at $m_0 = 0.1 \Msun$ on the low
mass end and at $100 \Msun$ on the high mass end, where $\bar{m}_*$ =
0.35 $\Msun$ is the corresponding mean stellar mass.  Our optimistic
assumption of 100 per cent thermalization efficiency of stellar winds
is at least partially offset by our conservative assumption to neglect
energy input from core collapse supernovae, which contribute a
comparable energy injection rate to massive stellar winds.

@@

The rate of energy input from PMS winds, $\dot{e}_{\rm TO}(t) =
f_{8}\dot{\mathcal{E}}/\bar{m}_*$, is dominated by fast Wolf-Rayet
winds and core-collapse supernovae from massive stars ($M_{\star} >
8M_{\odot}$), where $f_{8} =2.6 \times 10^{-3}$ is the fraction of the
stellar mass with $M_{\star} > 8M_{\odot}$ for our assumed Salpeter
IMF.  Here $\dot{\mathcal{E}} (t)$ is the energy injection rate per
massive star, which we estimate as
\begin{align}
\dot{\mathcal{E}} (t)=  1.3 \times 10^{36} {\rm erg\,s^{-1}}
\begin{cases}
  1 & t<4 \times 10^6 {\rm yr}\\
  \left(\frac{t}{4 \times  10^6\,{\rm yr}}\right)^{-3.73} &  4\times
  10^{6} {\rm yr}  \le t \le 10^{8} {\rm yr}
  \times 10^6 {\rm yr},\\
  0 & t > 10^8 {\rm yr}
\end{cases}
\label{eq:voss}
\end{align}
based on the results of \citet{VossDiehl+:2009a} (their Fig.~7, top
panel), who use a population synthesis code to simulate the mass and
energy injection into the ISM from an OB association.  Although
equation~\eqref{eq:voss} is valid only for $t \lsim 10$ Myr, in
practice the precise functional form of $\dot{e}_{\rm TO}(t)$ is
generally unimportant for our purposes, so we adopt
equation~\eqref{eq:voss} as being valid for all times.

>>>>

In the case of a single impulsive burst of star formation, the mass
and energy injection rate per unit stellar mass at time $t$ after the
burst are given, respectively, by
\begin{align} 
  \dot{\bar{m}}(t) &= \frac{\Delta M(t) \mu|_{M_{\rm TO}(t)}
    \left|\dot{M}_{\rm TO}(t)\right| + f_{\rm MS} \int_{m_0}^{m_{\rm
        T}(t)} \dot{m}(\Mstar, t) \mu|_{\Mstar} {\rm d}\Mstar
  }{\bar{m}_*}\label{eq:mdotImp}
  \\
  \dot{\bar{e}}(t) &=f_{\rm OB} \, \dot{e}_{\rm OB}(t)+ f_{\rm MS}
  \int_{m_0}^{m_{\rm T}(t)} \frac{\vw^2(\Mstar, t) \dot{m}(\Mstar, t)
    \mu|_{\Mstar} {\rm d}\Mstar}{\bar{m}_*},
  \label{eq:edotImp}
\end{align} 
In the top line, the first and second terms correspond to contributions
from main sequence (MS) stars and post-main sequence (PMS) stars,
respectively. Here $\mu$ is the IMF, which we take to be of the
Salpeter form $\mu|_{\Mstar} \propto M_{\star}^{-2.35}$, truncated at
$m_0 = 0.1 \Msun$ on the low mass end and at $100 \Msun$ on the high
mass end, where $\bar{m}_*$ = 0.35 $\Msun$ is the corresponding mean
stellar mass. In practice the contribution of main sequence winds to
the mass budget is negligible, and so we drop the second term in
equation~\eqref{eq:mdotImp}.

The first term in equation~\eqref{eq:edotImp} corresponds energy
injection from massive O \& B stars, while the second term accounts
for energy injection from stars on the lower main sequence. Both terms
have a thermalization efficiency, $f$, which we talk to be $1$. Note
we do not account for energy from Type II supernovae. However, the
mass injection from type II supernovae is implicitly included in the
first term of equation~\eqref{eq:mdotImp}

Winds from lower main sequence stars only dominate the energy
injection a late times ~10 Gyr after an impulsive burst of star
formation. Even with 100\% thermalization efficiency these winds could
not thermally stabilize the CNM. Thus, we could not describe this
regime within our steady formalism.

@@

The rate of energy injection due to winds from massive
stars, $\dot{e}_{\rm OB}(t) = f_{8}\dot{\mathcal{E}}/\bar{m}_*$, where
$f_{8} =2.6 \times 10^{-3}$ is the fraction of the stellar mass with
$M_{\star} > 8M_{\odot}$ for our assumed Salpeter IMF.  Here
$\dot{\mathcal{E}} (t)$ is the energy injection rate per massive star,
which we estimate as
\begin{align}
\dot{\mathcal{E}} (t)=  1.3 \times 10^{36} {\rm erg\,s^{-1}}
\begin{cases}
  1 & t<4 \times 10^6 {\rm yr}\\
  \left(\frac{t}{4 \times  10^6\,{\rm yr}}\right)^{-3.73} &  4\times
  10^{6} {\rm yr}  \le t \le 10^{8} {\rm yr}
  \times 10^6 {\rm yr},\\
  0 & t > 10^8 {\rm yr}
\end{cases}
\label{eq:voss}
\end{align}
based on the results of \citet{VossDiehl+:2009a} (their Fig.~7, top
panel), who use a population synthesis code to simulate the mass and
energy injection into the ISM from an OB association. {\bf AG--should
  just truncate the energy injection at $10^7$ years. Explain why
  turn-off energy injection is negligible in lower mass stars.}
